\Large \bf Evaluating eBPF as a Platform for Congestion Control Algorithm

### 2024-12-11 paper/sections/evaluation.tex
feat: finished evaluation and conclusion sections

\subsection{Results}
The results of behavioral benchmarks are shown in Figure \ref{fig:behavioral}. From the graph, we can see that [to-be-added-conclusion]. The results of CPU benchmarks are shown in Figure \ref{fig:cpu}. The eBPF implementation of TCP Cubic achieved impressive CPU performance compared to the built-in Linux kernel networking stack implementation. CCP-Cubic from the CCP Project \cite{generic-cong-avoid} combined with the kernel module + netlink CCP datapath achieved slightly lower performance, where its median is at x percent of the full kernel implementation value. Our implementation of eBPFCCP ranked lower on the performance chart, but was still able to achieve y percent of the full kernel implementation value. Due to the relative comparability of CPU performance between the kernel and eBPF implementations of TCP Cubicm, we theorize the noticable gap between eBPFCCP and kernel module CCP was due to our choice of using unix pipes rather than netlink as a channel for communicating between the eBPFCCP and the user space program. \\
From these results, we can conclude that eBPF is a viable platform for the development CCAs. The negligible performance overhead when compared to the kernel native implementation is impressive, and suggests that eBPF-CCAs can possibly also be used as a long-term deployment option outside of research and development stages. 
\end{document}

>>>>

\subsection{Results}

\begin{figure}[t]
    \centering
        \includegraphics[width=\columnwidth]{img/cca-behavior-cwnd}
        \caption{snd-cwnd behavior of TCP Cubic across different platforms of implementation. Averaged over 20 trials.
        }\label{fig:cca-behavior-cwnd}
    \end{figure}

\begin{figure}[t]
    \centering
        \includegraphics[width=\columnwidth]{img/cca-behavior-bitrate}
        \caption{Bitrate behavior of TCP Cubic across different platforms of implementation. Averaged over 20 trials.
        }\label{fig:cca-behavior-bitrate}
    \end{figure}

\begin{figure}[t]
    \centering
        \includegraphics[width=\columnwidth]{img/cca-behavior-rtt}
        \caption{RTT behavior of TCP Cubic across different platforms of implementation. Averaged over 20 trials.
        }\label{fig:cca-behavior-rtt}
    \end{figure}

\begin{figure}[t]
    \centering
        \includegraphics[width=\columnwidth]{img/cca-performance}
        \caption{Standard box plot of TCP Cubic CPU performance across different platforms of implementation. Higher is better. Box extends from 25th to 75th percentile. Whiskers extend to the farthest data point within 1.5 IQR from the box. Data gathered over 20 trials.
        }\label{fig:cca-performance}
    \end{figure}

The results of behavioral benchmarks are shown in Figures~\ref{fig:cca-behavior-cwnd},~\ref{fig:cca-behavior-bitrate}, and~\ref{fig:cca-behavior-rtt}. From the graph, we can see that the behavior of the same Congestion Control Algorithm remains similar across multiple platforms of integration. These results gives us confidence on the correctness of all the implementation platforms involved, and allows us to proceed to performance benchmarking. The results of CPU benchmarks are shown in Figure \ref{fig:cca-performance}. The eBPF implementation of TCP Cubic achieved impressive CPU performance compared to the built-in Linux kernel networking stack implementation. CCP-Cubic from the CCP Project \cite{generic-cong-avoid} combined with the kernel module + netlink CCP datapath achieved slightly lower performance, where its median is at x percent of the full kernel implementation value. Our implementation of eBPFCCP ranked lower on the performance chart, but was still able to achieve y percent of the full kernel implementation value. Due to the relative comparability of CPU performance between the kernel and eBPF implementations of TCP Cubicm, we theorize the gap between eBPFCCP and kernel module CCP was due to our choice of using unix pipes rather than netlink as a channel for communicating between the eBPFCCP and the user space program. \\
From these results, we can conclude that eBPF is a viable platform for the development CCAs. The negligible performance overhead when compared to the kernel native implementation is impressive, and suggests that eBPF-CCAs can possibly also be used as a long-term deployment option outside of research and development stages. With regards to CCP, while the performance overhead of eBPFCCP is non-negligible, it should be noted that the benchmark is performed on a single core VM. In a real-world scenario, the performance overhead of eBPFCCP is likely to be negligible for all but the most performance-sensitive industry networking applications. The safety guarantees provided by eBPFCCP would provide a good intermediate step for users to adopt and experiment with a new CCA before it is natively implemented either directly into the kernel or as an eBPF program. 
\end{document}
